Evaluation of Cache-Oblivious Data Structures

### 2008-05-09 paper/paper.tex
Added Makefile for building model bytecode from PROMELA source.

\begin{abstract}
% TODO: rewrite (NB: max. 10 lines)
%In modern computer hardware architecture, memory is organized in a hierarchy
consisting of several types of memory with different memory sizes, block
transfer sizes and access times. The cache-oblivious model has been proposed
to reflect this reality more accurately than traditional models. A number of
algorithms and data structures have been proposed that perform optimally in
this model. The goal of the proposed research project is to implement a
selection of cache-oblivious set-like data structures, evaluate their
performance (in terms of execution time and memory use) in a realistic
environment, and compare their performance to traditional data structures.
\end{abstract}

@@

\section{Introduction}
% Copy and shorten introduction from proposal
% -> Motivate research into cache-efficient algorithms
% -> Move "classification" subsection describing three models to front
% -> Describe each of the three models
% -> Introduce three data structures:
%     - note that hash tables have poor locality of reference
%     - note that btrees have good locality of reference but require pagesize
% -> Finally, present goal of the research (incorporate "Research Questions" in
proposal)

@@

% sparse array
% configurable density parameter
% binary search tree index
% van Emde Boas lay-out
% special optimization on insertion (note that it's not described by Bender)

>>>>

\begin{abstract}
% TODO: rewrite (NB: max. 10 lines)
%In modern computer hardware architecture, memory is organized in a hierarchy
%consisting of several types of memory with different memory sizes, block
%transfer sizes and access times. The cache-oblivious model has been proposed
%to reflect this reality more accurately than traditional models. A number of
%algorithms and data structures have been proposed that perform optimally in
%this model. The goal of the proposed research project is to implement a
%selection of cache-oblivious set-like data structures, evaluate their
%performance (in terms of execution time and memory use) in a realistic
%environment, and compare their performance to traditional data structures.
\end{abstract}

@@

\section{Introduction}
% Copy and shorten introduction from proposal
% -> Motivate research into cache-efficient algorithms
% -> Move "classification" subsection describing three models to front
% -> Describe each of the three models
% -> Introduce three data structures:
%     - note that hash tables have poor locality of reference
%     - note that btrees have good locality of reference but require pagesize
% -> Finally, present goal of the research (incorporate "Research Questions" in
% proposal)

@@

% sparse array
% configurable density parameter
% note that equal division of gaps over all windows is important
%   (and note the problems with the "old" behaviour)
% binary search tree index
% van Emde Boas lay-out
% special optimization on insertion (note that it's not described by Bender)
